\documentclass{resume} % Use the custom resume.cls style

\newcommand{\AuthorName}{Darien J. Morrow}
\newcommand{\AuthorLastName}{Morrow } % for footer. 
\newcommand{\resumetype}{Resume. }

\name{\AuthorName}
%\address{Postdoctoral Appointee at Argonne National Laboratory's Center for Nanoscale Materials}


\address{\href{mailto:darienmorrow@gmail.com}{\texttt{darienmorrow@gmail.com}} $\vert$ \href{mailto:dmorrow@anl.gov}{\texttt{dmorrow@anl.gov}} $\vert$
	1-816-752-4270} 




\begin{document}

%I inhabit the interface between high-dimensional data acquisition and physical model creation with verification by numerical simulation. 

I build computationally reproducible acquisition, analysis, simulation, and representation pipelines using Python.
I am interested in spectroscopy, nonlinear optics, lasers, magnetic resonance, and algorithm development.





   

\begin{rSection}{Education \& Work}

\begin{rSubsection}{Center for Nanoscale Materials at Argonne National Laboratory}{2020 - Present}{Postdoctoral Appointee supervised by Xuedan Ma}{Lemont, IL}
	\item Researching doped low-dimensional materials as RF to NIR transducers for Quantum Information Science.
	\item Building a cryogenic, paramagnetic spin resonance microscope.
	\item Modeling nanolasers, noise sources \& transients in single-photon detectors, exciton trapping, and RF antennas  
\end{rSubsection}

\begin{rSubsection}{University of Wisconsin--Madison}{2015 - 2020}{PhD: Physical Chemistry. \emph{Advised by John C. Wright.} \emph{GPA: 4.0/4.0} }{Madison, WI}
	\item Pioneered harmonic generation as an ultrafast probe of semiconductor symmetry and excited state dynamics.\\ Work culminated in \emph{U.S. Patent 10,823,664  Ultrafast, multiphoton-pump, multiphoton-probe spectroscopy}.
	\item Analyzed/modeled data for wide variety of materials chemistry projects in collaboration with Song Jin group. 
	\item Contributed to open source software projects. c.f. \href{http://wright.tools}{\texttt{wright.tools}} and \href{http://doi.org/10.21105/joss.01141}{\texttt{DOI: 10.21105/joss.01141}}
	\item Responsible for maintenance and furtherance of custom ultrafast laser systems including construction of new optomechanical \& electronic hardware, training new users, and troubleshooting hardware \& software

\end{rSubsection}

\begin{rSubsectionlistless}{Missouri Western State University}{2011-2015}{BS (Honors): Chemistry; Minors: Mathematics \& Physics. \emph{GPA: 4.0/4.0}}{Saint Joseph, MO} 
\end{rSubsectionlistless}



\end{rSection}


%\begin{rSection}{Research \& Work Experience}



%\begin{rSubsection}{Christopher G. Elles Research Group}{2014}{REU Fellow}{Lawrence, KS}
%	\item Investigated the excited state dynamics of substituted thiophene photo-rearrangement reactions
%	\item Developed and implemented reaction quantum yield measurement technique
%	\item Used ultrafast transient absorption spectroscopy to probe singlet and triplet excited state manifolds
%\end{rSubsection}


%\begin{rSubsectionlistless}{Morrow Contracting and Construction LLC}{2011 - 2015}{Skilled Laborer}{Saint Joseph, MO}
%\end{rSubsectionlistless}

%\end{rSection}
\iffalse
\begin{rSection}{Software Skills}
	\begin{itemize}[leftmargin = 0 pt]
		\item Python and the scientific Python software stack (numpy, matplotlib, scipy, h5py)
		\item Working knowledge: Arduino, Git, Latex, Autodesk Inventor
		\item Active contributor/maintainer of open source projects:
		\begin{itemize}
			\item \href{http://wright.tools}{\texttt{WrightTools}} (library): loading, processing, and plotting of multidimensional spectroscopy data 
			\item \href{http://github.com/wright-group/PyCMDS}{\texttt{PyCMDS}} (application): orchestrating many pieces of hardware into multidimensional spectrometers  
			\item \href{http://github.com/wright-group/attune}{\texttt{attune}} (library): tuning/calibrating multidimensional spectrometers
		\end{itemize}
		
	\end{itemize}	
\end{rSection}
\fi

%\begin{rSection}{Patents}
%	\begin{etaremune}
%		\item[$\cdot$] \textit{U.S. Patent 10,823,664} \textbf{Morrow, D. J.}; Kohler, D. D.; Wright, J. C. Ultrafast, multiphoton-pump, multiphoton-probe spectroscopy. 		
%	\end{etaremune}	
%\end{rSection}



\begin{rSection}{Publications}
	
\begin{etaremune}[topsep=0pt,itemsep=0pt,partopsep=0pt,parsep=0pt]


\item[$\cdot$] \textit{In preparation:} \textbf{Morrow, D. J.}; Room temperature paramagnetic spins in carbon nanotubes with sp\textsuperscript{3} defects.

\item[$\cdot$] \textit{In preparation:} \textbf{Morrow, D. J.};  Coherent modulation of broadband optical harmonic generation in graphene.

\item[$\cdot$] \textit{In preparation:} \textbf{Morrow, D. J.}; Ferrimagnetic states with tunable, chiral emission in layered BaFMn\textsubscript{0.5}Te.

\item[$\cdot$] \textit{In preparation:} \textbf{Morrow, D. J.}; Modulation of carbon nanotube emission with GHz split ring resonators. 

\item[$\cdot$] \textit{In preparation:} \textbf{Morrow, D. J.}; Ultrafast dynamics of WS\textsubscript{2}-MoS\textsubscript{2} Lateral Heterojunctions.

\item[$\cdot$] \textit{Submitted:} Kohler, D. D.; \textbf{Morrow, D. J.};  Spatially Resolved Spectroscopy Reveals the Disorder of WS\textsubscript{2}-MoS\textsubscript{2} Lateral Heterojunctions.

\item[$\cdot$] \textit{Submitted:} Lu, S.\textsuperscript{$\dagger$}; \textbf{Morrow, D. J.}\textsuperscript{$\dagger$}; et. al.  Encapsulating Semiconductor Quantum Dots in Supramolecular Cages Enables Ultrafast Guest–Host Electron and Vibrational Energy Transfer. $\dagger$: equal author contribution 

\item[$\cdot$] \textit{Submitted:} \textbf{Morrow, D. J.}; Ma, X. Noisy detectors with unmatched detection efficiency thwart identification of single photon emitters via photon coincidence correlation. \href{http://arxiv.org/abs/2204.07654}{\texttt{arXiv:2204.07654}}.

\item[$\cdot$] \textit{Submitted:} \textbf{Morrow, D. J.}; Ma, X. Facile reconstruction of time-resolved fluorescence data with exponentially modified Gaussians. \href{http://arxiv.org/abs/2201.03561}{\texttt{arXiv:2201.03561}}.

\item Chen, J-S.; et. al. Room Temperature Lasing from Semiconducting Single-Walled Carbon Nanotubes. \emph{ACS Nano}. \href{https://doi.org/10.1021/acsnano.2c06419}{\texttt{DOI: 10.1021/acsnano.2c06419}}. \textbf{2022}.

\item \textbf{Morrow, D. J.}; Ma, X. Trapping Interlayer Excitons in van der Waals Heterostructures by Potential Arrays.  \emph{PRB}. \href{https://journals.aps.org/prb/abstract/10.1103/PhysRevB.104.195302}{\texttt{DOI: 10.1103/PhysRevB.104.195302}}. \textbf{2021}.


\item Lohmann, S.;  et. al. Brightening of Dark States in CsPbBr\textsubscript{3} Quantum Dots Caused by Light-Induced Magnetism. \emph{Small}. \href{https://doi.org/10.1002/smll.202101527}{\texttt{DOI: 10.1002/smll.202101527}}. \textbf{2021}


\item  Pan, D.;  et. al. Deterministic fabrication of arbitrary vertical heterostructures of 2D Ruddlesden-Popper halide perovskites.  \emph{Nature Nanotechnology}. \href{https://doi.org/10.1038/s41565-020-00802-2}{\texttt{DOI:10.1038/s41565-020-00802-2}}. \textbf{2020}


\item \textbf{Morrow, D. J.}; et. al.	Quantum interference between the optical Stark effect and resonant harmonic generation in WS\textsubscript{2}.  \emph{PRB}. \href{https://journals.aps.org/pra/abstract/10.1103/PhysRevB.102.161401}{\texttt{DOI: 10.1103/PhysRevB.102.161401}}. \textbf{2020}.

\item \textbf{Morrow, D. J.}; et. al. Disentangling Second Harmonic Generation from Multiphoton Photoluminescence in Halide Perovskites using Multidimensional Harmonic Generation. \emph{JCPL}.\\ \href{https://pubs.acs.org/doi/10.1021/acs.jpclett.0c01720}{\texttt{DOI:10.1021/acs.jpclett.0c01720}}. \textbf{2020}

\item Hautzinger, et. al. Band Edge Tuning of 2D Ruddlesden-Popper Perovskites by A Cation Size Revealed through Nanoplates. \emph{ACS Energy Lett.}. \href{https://pubs.acs.org/doi/10.1021/acsenergylett.0c00450}{\texttt{DOI:10.1021/acsenergylett.0c00450}}. \textbf{2020}. 

\item  \textbf{Morrow, D. J.}; et. al. Triple sum frequency pump-probe spectroscopy of transition metal dichalcogenides. \emph{PRB}. \href{https://journals.aps.org/pra/abstract/10.1103/PhysRevB.100.235303}{\texttt{DOI: 10.1103/PhysRevB.100.235303}}. \textbf{2019}.

\item Thompson, B. J.; et. al. % Kohler, D. D.; Wright, J.C. 
WrightTools: a Python package for multidimensional spectroscopy \emph{JOSS}. 
\href{http://doi.org/10.21105/joss.01141}{\texttt{DOI: 10.21105/joss.01141}}. \textbf{2019}.
	
\item \textbf{Morrow, D. J.}; et. al. %Kohler, D. D.; Czech, K. J.; Wright, J. C. 
Multidimensional Triple Sum-Frequency Spectroscopy of MoS\textsubscript{2} and Comparisons with Absorption and Second Harmonic Generation Spectroscopies. \emph{JCP}. \href{http://doi.org/10.1063/1.5047802}{\texttt{DOI: 10.1063/1.5047802}}. \textbf{2018}.
	
\item \textbf{Morrow, D. J.}; et. al. % Kohler, D. D.; Wright, J. C. 
Group and phase velocity mismatch fringes in triple sum-frequency spectroscopy. \emph{PRA}. \href{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.96.063835}{\texttt{DOI: 10.1103/PhysRevA.96.063835}}. \textbf{2017}.

\item Fu, Y.;  et. al. %Hautzinger, M. P.; Zhao, Y.; Manger, L. H.; Wright, J. C.; Goldsmith, R. H.; Jin, S. 
Selective Stabilization and Photophysical Properties of Metastable Perovskite Polymorphs of CsPbI\textsubscript{3} in Thin Films. \emph{Chem. Mater.} \href{http://pubs.acs.org/doi/10.1021/acs.chemmater.7b02948}{\texttt{DOI: 10.1021/acs.chemmater.7b02948}}. \textbf{2017}. 
 
\item Chen, J.; \textbf{Morrow, D. J.}; et. al. % Fu, Y.; Zheng, W.; Zhao, Y.; Dang, L.; Stolt, M. J.; Kohler, D. D.; Wang, X.; Czech, K. J.; Hautzinger, M. P.; Shen, S.; Guo, L.; Pan, A.; Wright, J. C.; Jin, S. 
Single-Crystal Thin Films of Cesium Lead Bromide Perovskite Epitaxially Grown on Metal Oxide Perovskite (SrTiO\textsubscript{3}). \emph{JACS} \href{http://pubs.acs.org/doi/10.1021/jacs.7b07506}{\texttt{DOI: 10.1021/jacs.7b07506}}. \textbf{2017}. 
	



\end{etaremune}

\end{rSection}



\iffalse
\begin{rSection}{Teaching Experience}
	
	\begin{rSubsectionlistless}{Physical Chemistry: Thermodynamics}{Fall 2016}{Teaching Assistant for Prof. Gilbert M. Nathanson }{Madison, WI}
	\end{rSubsectionlistless}
	
	\begin{rSubsectionlistless}{General Chemistry}{Fall 2015 - spring 2016}{Teaching Assistant for Prof. Ive Herman and Dr. Paul Hooker}{Madison, WI}
	\end{rSubsectionlistless}
	
	\begin{rSubsectionlistless}{Organic Chemistry II}{Fall 2013}{Teaching Assistant for Prof. Steven P. Lorimor}{Saint Joseph, MO}
	\end{rSubsectionlistless}
	
\end{rSection}
\fi

\begin{rSection}{Service Activities \& Community Involvement}
	
	\begin{itemize}[leftmargin = 0 pt]
		\item Member of ANL's Nanoscience and Technology
		Diversity, Equity, and Inclusion Working Group. 2021-present 
		\item Volunteer with the Palos Restoration Project and the Forest Preserves of Cook County. 2021-present
		\item Reviewer for \emph{Journal of Chemical Physics} and \emph{Physical Review Letters}
		\item Hosted ``Detector Building'' at the Wisconsin Science Olympiad Regional Tournament. 2020
		\item Organized physical chemistry seminar series. 2018-2019
		\item Moderated the annual Wisconsin Middle School Science Bowl (sponsored by the DOE). 2017-2020
		\item Taught/supervised electronics for a week to high schoolers in the PEOPLE program. 2017
		\item Served on panels for UW \& KU REU students to discuss graduate school and careers. 2017 \& 2022 
		\item Served as vice-president (2014-2015) and member of MWSU's ACS affiliated Chemistry club. This included organizing community events like Super Science Saturday and Chemathon at MWSU. 2011-2015
	\end{itemize}
\end{rSection}

\begin{rSection}{Fellowships, Awards, \& Honors}

\begin{itemize}[leftmargin = 0 pt]
	\item (One of three finalists) APS Justin Jankunas Doctoral Dissertation Award in Chemical Physics. 2021.
	\item Richard and Joan Hartl Award for Research Excellence in Physical Chemistry. 2020.
	\item Roger Carlson Memorial Award for Excellence in Analytical Chemistry. 2018.
	\item Link Foundation Energy Fellowship (full graduate school stipend). July 2018 - June 2020. 
	\item NSF Graduate Research Fellowship Program, Honorable mention. 2017.
	\item MWSU Department of Chemistry, Edgar C. Little Outstanding Student Award. 2015.
	\item ACS Division of Analytical Chemistry, Undergraduate Award in Analytical Chemistry. 2015. 
	\item ACS Division of Inorganic Chemistry, Undergraduate Award in Inorganic Chemistry. 2013.
	\item MWSU President’s Honor’s List. Fall 2011 - spring 2015.
	\item NSF funded Midwest Apex Project scholarship. Fall 2011 - spring 2015.
	\item Golden Griffon Honors scholarship. Fall 2011 - spring 2015.
\end{itemize}
\end{rSection}


%\newpage



\end{document}
